\section{Related Work}

The most common method to decouple the UAV attitude states from the sensor today is to equip the aircraft with a gimbal, which results in easy UAV operation without losing track of the features that is to be observed. However, the gimbal angles have limited range and if the UAV angles are to big the features may be lost from the sensor field of view (FOV). Optimization may be used to create trajectories that ensure that the camera stays focused on the object \cite{nundalSKJONG}. Another solution that uses optimization without the use of gimbal is to put constraints on the the UAVs roll angle and altitude \cite{constraintsEGBERT}.

A simpler solution to avoid lateral movements of the FOV is to change the UAV course by using the rudder instead of the ailerons. The rudder deflection creates a yawing moment \cite{ratcFISHER} which causes the aircraft to change course. This type of controller is referred to both as a Rudder Augmented Trajectory Correction (RATC) controller \cite{ratcFISHER} and a skid-to-turn (STT) controller \cite{skidMILLS}. Results show that the performance of these controllers are comparable to conventional controllers using roll to change course, and that errors in the images is greatly reduced \cite{ratcFISHER}\cite{skidMILLS}\cite{alternateAHSAN}.

While the controllers offer a solution to the control problem that reduces the errors in the images, they do not ensure that the ground path that is to be observed will always stay inside the sensors FOV. Optimization is a commonly used method for ensuring that the application succeeds at some "outside" goal, and can be used to e.g. minimize the risk of being identified by radars \cite{radarINANC} or plan a path that ensures that a slung load attached to a helicopter do not collide with obstacles \cite{slungANDERSLACOUR}. The use of optimization to minimize the error of the sensor footprint for a fixed camera has been done by Jackson \cite{optimJACKSON}, by using on-board motion planning.

Jackson presents a path planner that aims to minimize the error between the target on the ground, and the footprint of a camera fixed to a UAV by using a Nonlinear Model Predictive Controller (NMPC). The NMPC is compared to a PID and a sliding-mode controller that seek to follow the same path. Simulations of the three controllers show that while the PID controller had much bigger crosstrack errors than the other two, the NMPC and the sliding-mode controller had similar performance. Simulations proved that the NMPC controller was able to find a near optimal solution with the performance characteristics of a real-time application.

One important point made by Jackson is that perfect tracking of a ground path with a fixed camera is not possible, as the controller that attempts to solve this would be unstable. The reason for this is the camera positions dependence on the roll angle. When the path turns right and the aircraft rolls right to follow this path, the camera position will move left, away from the path. This only applies to controllers that attempt a perfect tracking of the path, so that a near-perfect tracking is still achievable.